### 2021-07-15 doc/thesis/chapters/implementation.tex
tb

@@

However, in the development of hardware with any hardware description language (HDL), this is not possible.
HDL languages provide a syntax and semantic representation that allow to create parallel structures and a dependency on timing, such as a system clock.
Before this code can be run on the target hardware, i.e. an FPGA, it needs to run through a process called synthesis.
In synthesis, the HDL code is translated into a netlist and is consequently mapped into hardware logic cells that are available in the target device.
Various optimizations are done during this process, so that the direct connection to the code representation is lost.
Additionally, it is impossible to access every single signal within the design during debugging on the hardware, which probably is one of the main issues.
Synthesis tools like Xilinx Vivado provide support to make debugging possible in hardware, but require a large effort to implement them.
Another big factor that speaks against debugging in hardware, is that the process of synthesis takes a comparably large amount of time to transform code into the target technology.
Each time the code is adapted, the entire synthesis process needs to be started over.

@@

Thus, in order to allow debugging and verification of HDL code, the technology of simulation was invented.
Here, the HDL is also translated into a netlist that represents all the parallel processes just as in hardware, but the subsequent step of synthesis is not taken.
Therefore, simulation comes to a result much faster.
Since HDL designs actually only consist of electrical wires and some blocks (todo richtiges wort?), it is difficult to verify correct values.
The testbench environment is a very important factor in any project that includes hardware description language (HDL) code.
The reason therefor is that debugging

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Simulation Testbench}

The general significance of a simulation testbench in hardware description language (HDL) design is explained here, as well as an introduction to the used testbench framework that is used in this project.

%%%%%%%%%%%%%
\subsubsection{General}

@@

However, in the development of hardware with any HDL, this is not possible.
HDL languages provide a syntax and semantic representation that allow to create parallel structures and a dependency on timing, such as a system clock.
The design is based on signals that perform logic operations and transfer values into registers.
Thus, HDL code is often called register-transfer level, or short, RTL code.
Before this code can be run on the target hardware, i.e. an FPGA, it needs to run through a process called synthesis.
In synthesis, the HDL code is translated into a netlist and is consequently mapped into hardware logic cells that are available in the target device.
Various optimizations are done during this process, so that the direct connection to the code representation is lost.
Additionally, it is impossible to access every single signal within the design during debugging on the hardware, which is probably also one of the main issues.
Synthesis tools like Xilinx Vivado provide support to make debugging possible in hardware, but require a large effort to implement them, especially in terms of synthesis time.
Another big factor that speaks against debugging in hardware generally, is that the process of synthesis takes a comparably large amount of time to transform code into the target technology.
Each time the code is adapted, the entire synthesis process needs to be started over again.

@@

Thus, in order to allow debugging and verification of HDL code, the technology of simulation was invented.
Here, the HDL is also translated into a netlist that represents all the parallel processes just like in hardware, but the subsequent step of synthesis is not taken.
Therefore, simulation comes to a result much faster.
Since HDL designs actually only consist of electrical wires and some basic block primitives, like Flipflops or lookup tables, it is difficult to verify correct values.
They would need to be compared in their binary bit-pattern format, at the correct point in time.
Of course the HDL language provides support with different datatypes, that abstract the binary number representation and make the numbers human-readable.
However, it remains an enormous effort to manually write testing code to verify a bus interface, for example.
In order to simplify such complex operations, various testbench frameworks are available to developers.

%%%%%%%%%%%%%
\subsubsection{Simulator GHDL}

%%%%%%%%%%%%%
\subsubsection{Framework cocotb}

\cite{cocotbDoc}.
